---
title: "Chapter4_RevisitingProbability"
author: "LA"
date: "2024-03-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
set.seed(1409)
library("tidyverse")
sample(c("HEADS", "TAILS"), 10, TRUE) 
```
```{r}
sample(0:1, 10, TRUE) %>% sum() 
```
```{r}
heads10k <- replicate(10000, sample(0:1, 10, TRUE) %>% sum())   
```

```{r}
data10k <- tibble(heads = heads10k) %>%       # creating a tibble/data frame
                group_by(heads) %>%           # group by number of possibilities
                summarise(n = n(), p=n/10000) # count occurences of possibility,
                                              # & calculate probability (p) of
                                              # each
```

```{r}
ggplot(data10k, aes(heads,p)) + 
  geom_col(fill = "skyblue") + 
  labs(x = "Number of Heads", y = "Probability of Heads in 10 flips (p)") +
  theme_bw() +
  scale_x_discrete(limits=0:10)
```
dbinom(x, size, prob) -> This function gives you probability of 'x' occurring given a set 'size' and given its probability of happening in a single trial.
```{r}
dbinom(3, 10, 0.5)
```

```{r}
dbinom(0:10, 10, 0.5)
```

```{r}
dbinom(0:3, 10, 0.5) %>% sum()
```

```{r}
pbinom(3, 10, 0.5, lower.tail = TRUE)  
```

```{r}
pbinom(50, 100, 0.5, lower.tail = FALSE) 
```

```{r}
p1 <- pbinom(49, 100, .5, lower.tail = TRUE)
p1
```

```{r}
qbinom(p1, 100, .5, lower.tail = TRUE)
```
```{r}
qbinom(.1, 17, 0.5, lower.tail = TRUE) 
```

# 4.3.3.1 Task 1: Standard Deviations and IQ Score Distribution
```{r}

IQ_data <- tibble(IQ_range = c(40, 160))

ggplot(IQ_data, aes(IQ_range)) + 
  stat_function(fun = dnorm, args = list(mean = 100, sd = 10)) +
  labs(x = "IQ Score", y = "probability") +
  theme_classic()

```
# 4.3.3.2 Task 2: Changing Range and Step Size of The Normal Distribution
```{r}
ND_data <- tibble(ND_range = seq(-4, 4, 0.01))
ggplot(ND_data, aes(ND_range)) + 
  stat_function(fun = dnorm, args = list(mean = 0, sd = 1)) +
  labs(x = "SD units", y = "probability", title = "The Normal Distribution") +
  theme_classic()
```

# 4.3.4.1 Task 3: Calculating Cumulative Probability of Height
```{r}
pnorm(190, 170, 7, lower.tail = FALSE)
```

```{r}
pnorm(185, 170, 7, lower.tail = FALSE)
```
# 4.3.5.1 Task 5: Using pnorm() and qnorm() to find probability and cut-off values
```{r}
qnorm(0.95, 100, 15) 
pnorm(105, 100, 15, lower.tail = FALSE) - 
  pnorm(110, 100, 15, lower.tail = FALSE)
```



