---
title: "Chapter5_NHST"
author: "LA"
date: "2024-03-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries 
```{r}
library("tidyverse")
```

# 5.4.1 Task 1: Creating a Dataframe
```{r}
participants_list <- c(1:22)
participants_rt <- c(631.2, 800.8, 595.4, 502.6, 604.5, 516.9, 658.0, 502.0, 496.7, 600.3, 714.6, 623.7, 634.5, 724.9, 815.7, 456.9, 703.4, 647.5, 657.9, 613.2, 585.4, 674.1)
ns_data <- tibble(participant = participants_list, valid_rt = participants_rt)
```

# 5.4.2 Task 2: Comparing Original and New Sample Reaction Times
```{r}
woods_mean <- 590
n_participants <- ns_data %>% filter(ns_data$valid_rt > woods_mean) %>% nrow() 
```
# 5.4.3 Task 3: Calculating Probability
```{r}
sum(dbinom(n_participants:nrow(ns_data), nrow(ns_data), .5))
```
#5.5.1 Task 4: Calculating the Mean and Standard Deviation
```{r}
ns_data_mean <- summarise(ns_data, mean = mean(participants_rt)) %>% pull(mean)
ns_data_sd <- summarise(ns_data, sd = sd(participants_rt)) %>% pull(sd)
  
```
# 5.5.2 Task 5: Calculating the Observed Test Statistic
```{r}
t_obs <- (ns_data_mean - woods_mean) / (ns_data_sd / sqrt(nrow(ns_data)))
```
# 5.5.3 Task 6: Comparing the Observed Test Statistic to the t-distribution using pt()
```{r}
pval <- pt(t_obs, nrow(ns_data)-1, lower.tail = FALSE) * 2
```
# 5.5.4 Task 7: Comparing the Observed Test Statistic to the t-distribution using t.test()
```{r}
t.test(ns_data$valid_rt, mu = woods_mean)
```
# 5.5.5 Task 8: Drawing Conclusions about the new data
```{r}

```


